An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-12-13 jmiv.tex
Further corrections

Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the \revision{signed} Euclidean distance transformation with respect to shape $S$. The value $d_S(p)$ gives the Euclidean distance between \revision{$p \notin S$ and the closest pixel in $S$. For points $p \in S$, $d_S(p)$ gives the distance between $p$ and the closest pixel not in $S$.}

\begin{definition}[m-Ring Set]
\revision{
Given a digital shape $S\in\Omega$, its signed distance transformation $d_S$ and natural number $m \neq 0$, the {\em $m$-ring set of $S$} is defined as
\begin{align*}
	\mathcal{R}_m(S) &:= \mathcal{L}_m \cup \mathcal{L}_{-m},
\end{align*}
where
\begin{align*}
	\mathcal{L}_m(S) &:= \left\{ \quad \begin{array}{cc}
		\left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} & , \quad m>0\\
		\left\{ p \in \Omega \; | \; m+1 > d_S(p) \geq m \right\} & , \quad m<0
		\end{array} \right.
\end{align*}}
\end{definition}

@@

Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $n=50$.

@@

Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than its precedent.

\revision{
We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem. Injecting contour information leads to a third order model, which we prefer to avoid. Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.}

@@

\revision{
We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model (see figure \ref{fig:contour-info})}. Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
of a chosen ball and the area of the intersection of this ball with the shape.  In particular, regions of positive
curvature have fewer pixels in their intersection set than on its complement w.r.t the estimation ball. This implies
that variables in such regions are labeled with 1, as the unbalance grows otherwise. We attenuate curvature if we shift
the center of the estimation ball towards the interior of the shape, which means removing the 1-labeled pixels. That is
why we take the complement of the optimization solution.

>>>>

Let $d_{S}:\Omega \rightarrow \mathbb{R}$ be the \revision{signed} Euclidean distance transformation with respect to shape $S$. The value $d_S(p)$ gives the Euclidean distance between \revision{$p \notin S$ and the closest pixel in $S$. For points $p \in S$, $d_S(p)$ gives the distance between $p$ and the closest pixel not in $S$.}

\begin{definition}[m-Ring Set]
\revision{
Given a digital shape $S\in\Omega$, its signed distance transformation $d_S$ and natural number $m \neq 0$, the {\em $m$-ring set of $S$} is defined as
\begin{align*}
	R_m(S) &:= L_m \cup L_{-m},
\end{align*}
where
\begin{align*}
	L_m(S) &:= \left\{ \quad \begin{array}{cc}
		\left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} & , \quad m>0\\
		\left\{ p \in \Omega \; | \; m+1 > d_S(p) \geq m \right\} & , \quad m<0
		\end{array} \right.
\end{align*}}
\end{definition}

@@

Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$n=50$}.

@@

\revision{
Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica $S^{(i)}$.

We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem. Injecting contour information leads to a third order model, which we prefer to avoid. Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.}

@@

\revision{
We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because contour information is not included in the model (see figure \ref{fig:contour-info})}. Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
of a chosen ball and the area of the intersection of this ball with the shape.  In particular, regions of positive
curvature have fewer pixels in their intersection set than on its complement w.r.t the estimation ball. This implies
that variables in such regions are labeled with 1, as the unbalance grows otherwise. We attenuate curvature if we shift
the center of the estimation ball towards the interior of the shape, which means removing the 1-labeled pixels. That is
why we take the complement of the optimization solution.
